% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Qintong Wu}

\basicInfo{
  \email{qintongw@usc.edu} \textperiodcentered\ 
  \phone{(+1) 213-709-7290} \textperiodcentered\ 
  \linkedin[Qintong Wu]{https://www.linkedin.com/in/qintong-wu-9b5b43123/}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Southern California}, Los Angeles, U.S.}{2016 -- present}
\textit{Master} in Electronics Engineering (EE), expected May 2018
\datedsubsection{\textbf{Hangzhou Dianzi University}, Hangzhou, China}{2012 -- 2016}
\textit{B.S.} in Electronics Engineering (EE)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Synced Inc.} Toronto, Canada}{July. 2017 -- Present}
\role{Summer Intern}{Research Engineer}
Brief introduction: Working on Neural Machine Translation System(NMT) for English-Chinese(simplified) Translation problem. Currently, none of mainstream NMTs provides EN-ZH translation. We achieved a usable yet not perfect system with the best bleu score around 10 (on AI-related topics translation)
\begin{itemize}
  \item Implemented Neural Machine Translation system consists of encoder-decoder (LSTMs) architecture with attention mechanism
  \item Optimized for EN-ZH, scripts for Chinese corpus preparation
  \item Maintained system running on AWS server 
\end{itemize}

\datedsubsection{\textbf{Recommender System}}
\role{Java, Hadoop, Docker, Linux}{Individual Projects}
Brief introduction: Working on Netflix Prize Movie data, I configured a Hadoop cluster with one Master and five Slave, then build the system for recommending new movies based on users' previous rating history.
\begin{itemize}
  \item Constructed Rating Matrix for every single user and Co-occurrence Matrix for all movies from the raw data.
  \item Implemented Item Collaborative Filter using MapReduce Paradigm.
  \item Implemented Matrix Multiplication using MapReduce Paradigm.
  \item 4 MapReduce Jobs in total, with a bash script for running the system.
\end{itemize}

\datedsubsection{\textbf{Research on relation between Diabetes and Depression}}{Feb. 2017 -- May. 2017}
\role{Python, R, Linux}{Research Projects supervised by Prof. Raghu Raghavendra}
Brief introduction: Conducted research on data analysis and data modeling. Finally, my work figured out the key indicators for treatment assignment and built a RNN model for the further prediction based on patients' records.
\begin{itemize}
  \item Explored and cleaned dataset with Pandas module
  \item Estimated casual effects between Diabetes and Depression using Targeted Learning Method.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java == Python > C
  \item Platform: Mac OS, Ubuntu
  \item Development: Docker, Hadoop, Numpy, Pandas, Tensorflow
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
\datedline{Other awards}{2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: https://syncedreview.com/?s=Qintong+Wu
  \item GitHub: https://github.com/aracthon
  \item Languages: English - Proficiency, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
